Appendix: Luminance constancy under fixed geometry

### 2018-08-28 Draft6/appendix.tex
added figure to appendix

>>>>

\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Cone excitations}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_a.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Normalized contrast}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_b.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Normalized contrast.}
\label{fig:Condition1}
\end{figure}
